RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data

### 2015-04-27 paper/paper7/paper7.tex
section 4

\tb{Depending on individual use cases, validation environments should enable users to select which constraints to validate against.
For some use cases, validating $\mathcal{CT}_{B}$ constraints may be more important than validating $\mathcal{CT}_{S}$ or $\mathcal{CT}_{C}$ constraints.}

@@

The complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses three disjoint \emph{sets of constraint types}:
\begin{enumerate}
	\item \textbf{$\mathcal{CT}_{B}$: \emph{Basic Constraint Types}}
	\item \textbf{$\mathcal{CT}_{S}$: \emph{Simple Constraint Types}}
	\item \textbf{$\mathcal{CT}_{C}$: \emph{Complex Constraint Types}}
\end{enumerate}

The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to define vocabularies.
\emph{Basic constraint types} ($\mathcal{CT}_{B}$) 
denotes the set of constraint types whose constraints 
can be extracted completely automatically out of vocabularies.
As vocabularies have been specified using \emph{RDF}, \emph{RDFS}, and \emph{OWL},
\emph{basic constraints} ensure that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
%The {\em existential quantification} (\emph{R-86}) 
%\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (\emph{DL}), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
\emph{Minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
This way, it is expressible in OWL 2 that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
\begin{ex}
[   a owl:Restriction ; rdfs:subClassOf TableStructure ;
    owl:minQualifiedCardinality 1 ;
    owl:onProperty column ;
    owl:onClass Column ] .
\end{ex}

\emph{Simple constraint types} ($\mathcal{CT}_{S}$) is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
The {\emph{data property facets} (\emph{R-46}) $\mathcal{CT}_{S}$ constraint type enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).

\emph{Complex constraint types} ($\mathcal{CT}_{C}$) encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
Complex constraints show the importance of constraint languages enabling to describe complex constraints.
For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
An example of such \emph{structure} constraints is that 
a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search.

\tb{refer to evaluation / what do we want to know?}

@@

%
%- different sets of constraints for different use cases / use case specific constraints
%
%- validation against minimal set of requirements / constraints
%
%-----

>>>>

@@

The complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses three disjoint \emph{sets of constraint types}:
\begin{enumerate}
	\item $\mathcal{CT}_{B}$: \textbf{\emph{Basic Constraint Types}}
	\item $\mathcal{CT}_{S}$: \textbf{\emph{Simple Constraint Types}}
	\item $\mathcal{CT}_{C}$: \textbf{\emph{Complex Constraint Types}}
\end{enumerate}

The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to define vocabularies.
\emph{Basic constraint types} ($\mathcal{CT}_{B}$) 
denotes the set of constraint types whose constraints 
can be extracted completely automatically out of vocabularies.
As vocabularies have been specified using \emph{RDF}, \emph{RDFS}, and \emph{OWL},
\emph{basic constraints} ensure that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
%The {\em existential quantification} (\emph{R-86}) 
%\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (\emph{DL}), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
\emph{Minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
This way, it is expressible in \emph{OWL 2} that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
\begin{ex}
[   a owl:Restriction ; rdfs:subClassOf TableStructure ;
    owl:minQualifiedCardinality 1 ;
    owl:onProperty column ;
    owl:onClass Column ] .
\end{ex}

\emph{Simple constraint types} ($\mathcal{CT}_{S}$) is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
{\emph{Data property facets} (\emph{R-46}) is an example of an $\mathcal{CT}_{S}$ constraint type which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).

\emph{Complex constraint types} ($\mathcal{CT}_{C}$) encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
Complex constraints show the importance of constraint languages enabling to describe more complex constraints.
For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
An example of such constraints of the constraint type \emph{structure} is that 
a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search.

@@

Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
For some use cases, 
validating constraints of $\mathcal{CT}_{B}$ constraint types may be more important than validating constraints of $\mathcal{CT}_{S}$ or $\mathcal{CT}_{C}$ constraint types.
For other use cases,
validating $\mathcal{SL}_{2}$ constraints may be sufficient without taking $\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$ constraints into account.
\tb{refer to evaluation / what do we want to know?} 
%
%- different sets of constraints for different use cases / use case specific constraints
%
%- validation against minimal set of requirements / constraints
%
%-----
